---
title: "mldoeR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mldoeR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mldoeR)
```

# Introduction

This is the `mldoeR` package. It contains a catalog of regular four-and-two-level designs.
It also contains useful functions to handle and analyze those designs.

# Search-table

For visualization purposes, you might want to generate a search-table.
The `searchTable()` function makes this possible for two-level designs.
The search-table for $2^{6-2}$ designs of resolution $III$ looks like this.

```{r}
st <- searchtable(k = 4, p = 2, R = 3)
print(st)
```
If you want to generate search-table for mixed-level designs, the `mSearchtable()` function is there.
For example, you can generate the search-table for $4^{1}2^{5}$ designs of resolution $III$ in $2^5$ runs.

```{r}
mST <- mixed_searchtable(m = 1, k = 5, p = 2, R = 3)
print(mST)
```

# Generators

In these search-table, the generators are presented as strings.
However, you can easily get the number representation of a generator, from its string, using the `char2num()` function.

```{r}
gen = "acd"
char2num(gen)
```

The `num2char()` function allows you to do the invert operation.

```{r}
num2char(13)
```

